Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2022-03-14 doc/manuscript/ESSDmanuscript.Rmd
work
revert commit
manuscript
Update ESSDmanuscript.Rmd

## Carbon stocks

Forest ecosystem C stocks may be parsed into pools in various ways. 
IPCC parses into biomass (aboveground and belowground), dead organic matter (dead wood and litter), and soil organic matter (Table&nbsp;\@ref(table_variables)).
Quantifying these requires a one-time measurement.

@@

Soil organic matter is defined as...

>>>>

## Carbon stocks
Forest ecosystem C stocks may be parsed into pools in various ways. 
IPCC parses into biomass (aboveground and belowground), dead organic matter (dead wood and litter), and soil organic matter (Table&nbsp;\@ref(table_variables)).
Quantifying these requires a one-time measurement.

@@

Soil organic matter is defined as "Includes organic carbon in mineral and organic soils (including peat) to a specified depth chosen by the country and
applied consistently through the time series. Live fine roots (of less than the suggested diameter limit for belowground biomass) are included with soil organic matter where they cannot be distinguished from it empirically."(2003 IPCc GPG for LULUCF (https://www.ipcc-nggip.iges.or.jp/public/gpglulucf/gpglulucf_files/Glossary_Acronyms_BasicInfo/Glossary.pdf)
